BlogForever Crawler: Techniques and Algorithms to Harvest the Modern Web

### 2013-11-01 tex/main.tex
Snapshot of the project as sent in the first email.
Add a few ideas from reading the WebDataExtraction,ApplicationsAndTechniques survey, add sripts to run and score theextraction methods.
New title idea.

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

\documentclass{acm_proc_article-sp}
\usepackage{epsfig}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{hyperref}
\newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
\newcommand{\surl}[1]{\urlstyle{ff}\url{#1}}

@@

\title{Web feed based content extraction with JavaScript rendering for the Invenio crawler}

@@

\author{
% 1st. author
\alignauthor
Blanvillain Olivier\\
       \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
       \affaddr{1014 Lausanne, Switzerland}\\
       \email{olivier.blanvillain@epfl.ch}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
}

>>>>

\documentclass{acm_proc_article-sp}

\usepackage{epsfig}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{hyperref}

\newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
\newcommand{\surl}[1]{\urlstyle{ff}\url{#1}}

@@

% \title{Web feed based content extraction with JavaScript rendering for the Invenio crawler}
\title{BlogForever Crawler: Techniques and Algorithms to Harvest the Modern Web}
% to Extract Data From the Modern Web}
% Modern Web Pages}

@@

\author{
% 1st. author
\alignauthor
Olivier Blanvillain\\
       \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
       \affaddr{1014 Lausanne, Switzerland}\\
       \email{olivier.blanvillain@epfl.ch}
% 2nd. author
\alignauthor
Nikos Kasioumis\\
       \affaddr{European Organization for Nuclear Research (CERN)}\\
       \affaddr{1211 Geneva 23, Switzerland}\\
       \email{nikos.kasioumis@cern.ch}
% 3rd. author
\alignauthor
Vangelis Banos\\
       \affaddr{Department of Informatics}\\
       \affaddr{Aristotle University of Thessaloniki, Greece}\\
       \email{vbanos@gmail.com}
}
